---
title: "ReESH Site Summary: US-MMS (Morgan Monroe State Forest"
output: html_document
theme: cerulean
---

<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
  }
td {  /* Table  */
  font-size: 8px;
}
h1.title {
  font-size: 38px;
  color: DarkRed;
}
h1 { /* Header 1 */
  font-size: 28px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size: 22px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Site: IU Growth Chambers
### Site Contact: Michael Benson IU micbenso@iu.edu

## Site Location

```{r, echo = FALSE, message = FALSE, warning = FALSE}
#knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
library(ggmap)
myMap <- get_stamenmap(bbox = c(left = -86.2131,
                                    bottom = 39.2232,
                                    right = -86.6131,
                                    top = 39.4232),
          maptype = "terrain", 
          crop = FALSE,
          zoom = 6)
###//Chechout the map
#ggmap(myMap)
##//AmeriFlux Tower Location
Tower_location <- data.frame(lon = c(-86.4131), lat = c(39.3232))

# create a map with a point location for boulder.
ggmap(myMap) + labs(x = "", y = "") +
  geom_point(data = Tower_location, aes(x = lon, y = lat), 
             color = "darkred", alpha = 0.7, size = 25, shape = "*",
             show.legend = FALSE) +
  guides(fill = FALSE, alpha = FALSE, size = FALSE)

###//For Ameriflux project Sites a second map will be included to represent specific sampling locations

##//Made up points to test mapping
myMap2 <- get_stamenmap(bbox = c(left = -86.4151,
                                    bottom = 39.3222,
                                    right = -86.4121,
                                    top = 39.3242),
          maptype = "terrain", 
          crop = TRUE,
          zoom = 9)
###//Chechout the map
#ggmap(myMap)


##//Made up points to test mapping
samp_location <- data.frame(Site = c("BC1", "BC4", "TDR1", "TDR2"),
                            lon = c(-86.413870, -86.414120, 
                                    -86.413685, -86.413186),
                            lat = c(39.323567, 39.323030, 
                                    39.322714, 39.323158))

# create a map with a point location for boulder.
ggmap(myMap2) + labs(x = "", y = "") +
  geom_point(data = samp_location, aes(x = lon, y = lat), 
             color = "darkblue", alpha = 0.7, size = 25, shape = "*",
             show.legend = FALSE) +
    geom_point(data = Tower_location, aes(x = lon, y = lat), 
             color = "darkred", alpha = 0.7, size = 25, shape = "*",
             show.legend = FALSE) +
  guides(fill = FALSE, alpha = FALSE, size = FALSE)


```
Samples were collected from Indiana University Greenhouses to represent the soils being used in the growth chambers

## Soil Texture

## Saturated Hydraulic Conductivity

## Soil Water Retention Curves

Van Genutchen Equation for soil water retention curves
$$
\theta=\theta_{r}+\left(\theta_{s}-\theta_{r}\right)\left[1+(\alpha \psi)^{n}\right]^{-(1-\frac{1}{n})}
$$

Van Genutchen Equation for soil water retention curves
$$
\psi=\frac{\sqrt[n]{\left(\frac{\theta_{s}-\theta}{\theta_{r}-\theta_{s}}\right)^{n /(n-1)}-1}}{\alpha}
$$

```{r, echo = FALSE, message = FALSE, warning = FALSE}
##//Data analysis of soil water retention curves
##//Section for estimating parameter coefficients needed for converting soil moisture to
      ##  soil matric potential

##//Modified from data management for Hyprop and WP4C scripts
##//Package management
library(readxl); library(tidyverse); library(lubridate); library(dplyr)
library(tidyr); library(tidyselect); library(stringr); library(tidybayes)
library(rstan); library(brms); library(modelr); library(sjPlot); library(sjstats)
library(MASS); library(scales); library(knitr); library(kableExtra)

##//ggplot theme 
theme_set(theme_minimal())

##//custom color ramp 
GoAvsGo <- c("#6F263D", "#236192", "#A2AAAD", "#000000")

##//Where is the data
##//List of files in the directory
Flist <- dir("D:/Dropbox/Projects/Indiana/SoilLab/Data/HyProp/HypropExports/Sites/MMSF", 
             pattern = ".xlsx")

##/ 1 Information
##/ 2 Measurements
##/ 3 Spline Points
##/ 4 Evaluation-WP4 manual
##/ 5 Evaluation-Retention
##/ 6 Evaluation-Conductivity
##/ 7 Evaluation-Conductivity
##/ 8 Fitting-Retention
##/ 9 Fitting-Conductivity
##/ 10 Fitting-Conductivity
##/ 11 Fitting-Parameter value
##/ 12 FittingCorrelationMatrix
##/ 13 Fitting-Statistical analysis
##/ 14 Base Points-Retention
k = 1
##//Meta Data
text <- read_xlsx(paste("D:/Dropbox/Projects/Indiana/SoilLab/Data/HyProp/HypropExports/Sites/MMSF", 
      Flist[k],  sep = "/"), sheet = 1)
##//Just WP4C data
wp4 <- read_xlsx(paste("D:/Dropbox/Projects/Indiana/SoilLab/Data/HyProp/HypropExports/Sites/MMSF", 
      Flist[k],  sep = "/"), sheet = 4)
##//All Raw data
dats <- read_xlsx(paste("D:/Dropbox/Projects/Indiana/SoilLab/Data/HyProp/HypropExports/Sites/MMSF", 
      Flist[k],  sep = "/"), sheet = 5)
##//Fitted Vanaguchen curves
fits <- read_xlsx(paste("D:/Dropbox/Projects/Indiana/SoilLab/Data/HyProp/HypropExports/Sites/MMSF", 
      Flist[k],  sep = "/"), sheet = 8)

##//Building the raw data dataframes
d_fit_out <- c()
d_raw_out <- c()
for(k in 1:length(Flist)){
  
text <- read_xlsx(paste("D:/Dropbox/Projects/Indiana/SoilLab/Data/HyProp/HypropExports/Sites/MMSF", 
      Flist[k],  sep = "/"), sheet = 1)
wp4 <- read_xlsx(paste("D:/Dropbox/Projects/Indiana/SoilLab/Data/HyProp/HypropExports/Sites/MMSF", 
      Flist[k],  sep = "/"), sheet = 4)

dats <- read_xlsx(paste("D:/Dropbox/Projects/Indiana/SoilLab/Data/HyProp/HypropExports/Sites/MMSF", 
      Flist[k],  sep = "/"), sheet = 5)
fits <- read_xlsx(paste("D:/Dropbox/Projects/Indiana/SoilLab/Data/HyProp/HypropExports/Sites/MMSF", 
      Flist[k],  sep = "/"), sheet = 8)

##//Isolating the meta data
Sample = text$Value[2]
MeasureStart = text$Value[3]
MeasureEnd = text$Value[4]
MeasureTime = text$Value[5]
Units = text$Value[6]
Software = text$Value[7]
GeomParameters = text$Value[8]
SoilSurfArea_cm2 = text$Value[9]
SoilColumnHeight_cm = text$Value[10]
Vol_cm3 = text$Value[11]
LowerTensiometer_cm = text$Value[12]
UpperTensiometer_cm = text$Value[13]
HYPROP_Parameters = text$Value[14]                                      
MeasurementHeadNetWeight_g = text$Value[15]                       
EmptySoilSamplingRingWeight_g = text$Value[16]                  
AirEntryPressureUpperTensiometer_bar = text$Value[17]         
AirEntryPressureLowerTensiometer_bar = text$Value[18]              
DensitySolidSubstance_g_cm3 = text$Value[19]                     
StatisticalAnalysis = text$Value[20]                                
Tensiometer_hPa = text$Value[21]                                      
Scale_g = text$Value[22]                                     
SensorUnitInformation = text$Value[23]                                 
Busnumber = text$Value[24]                                   
Subaddress = text$Value[25]                                             
SerialNumber = text$Value[26]                                           
SensorUnitName = text$Value[27]                                    
FirmwareVersion = text$Value[28]                                    
ScaleSerialNumber = text$Value[30]                                      
ScaleName = text$Value[31]                                            
Correction = text$Value[32]                                            
VolumeCorrection_ml = text$Value[33]                               
WeightCorrection_g = text$Value[34]                                   
StartStopLine = text$Value[35]                                        
Start = text$Value[36]                                          
TensionTopAirEntryPoint_Stopp = text$Value[37]                         
TensionBottomAirEntryPoint = text$Value[38]                              
CalculationWaterContents = text$Value[39]                             
CalculationWaterContents2 = text$Value[40]                             
InitialWaterContent_Vol_pct = text$Value[41]                               
DrySoilWeight_g = text$Value[42]                              
AdditionalSoilParamters = text$Value[43]                              
Density_g_cm3 = text$Value[44]                                
Porosity = text$Value[45]                                   
FittingParameters = text$Value[46]                                   
INTERPOL = text$Value[47]                                       
Tensiometer_Mean = text$Value[48]                                       
Polynomial_degree = text$Value[49]                                      
wtheta = text$Value[50]                                          
wk = text$Value[51]                                         
Fitting = text$Value[52]                                        
ModelDescription = text$Value[53]                                     
Notes = text$Value[54]                                    
GeneralData = text$Value[55]                                   
SiteCoordinates = text$Value[56]                                 
SamplingDate = text$Value[57]                               
SiteDescription = text$Value[58]                                  
SoilType = text$Value[59]                              
LandUse = text$Value[60]                               
SoilPhysicalData = text$Value[61]                           
Texture = text$Value[62]                        
SoilTextureClass = text$Value[63]                        
SamplingDepth = text$Value[64]                        
OrganicCarbonContent = text$Value[65]                   
SamplePrep = text$Value[66]                     
InitialSaturationTime = text$Value[67]                   
SwellingHandling = text$Value[68]  

dats <- read_xlsx(paste("D:/Dropbox/Projects/Indiana/SoilLab/Data/HyProp/HypropExports/Sites/MMSF", 
      Flist[k],  sep = "/"), sheet = 5)

fits <- read_xlsx(paste("D:/Dropbox/Projects/Indiana/SoilLab/Data/HyProp/HypropExports/Sites/MMSF", 
      Flist[k],  sep = "/"), sheet = 8)

d_raw <- data.frame(Sample = Sample, 
                    MPa = dats$`[MPa]`,
                    Vol_Water = dats$`Water Content [Vol%]`)

d_fit <- data.frame(Sample = Sample, 
                    MPa = fits$`[MPa]`,
                    Vol_Water = fits$`Water Content [Vol%]`)

d_fit_out <- rbind(d_fit_out, d_fit)
d_raw_out <- rbind(d_raw_out, d_raw)

}

###//Correct and add parameters
##//Observation Number
d_raw_out$SampleN <- as.numeric(as.factor(d_raw_out$Sample))
d_fit_out$SampleN <- as.numeric(as.factor(d_fit_out$Sample))

d_fit_out$MPa <- as.numeric(d_fit_out$MPa)
d_fit_out$SampleN <- as.numeric(d_fit_out$MPa)

d_fit_out$MPa_Log10 <- (log10(d_fit_out$MPa)) 
d_raw_out$MPa_Log10 <- log10(abs(d_raw_out$MPa)) 

d_raw_out$Vol_Water_d <- d_raw_out$Vol_Water / 100 
d_fit_out$Vol_Water_d <- d_fit_out$Vol_Water / 100 

##//Plot the METER curves with the raw data
ggplot() +
  
  geom_line(data = d_fit_out[d_fit_out$Vol_Water>0 & d_fit_out$Vol_Water_d<1 & 
                                d_fit_out$MPa_Log10>-4,], 
            aes(y = MPa, x = Vol_Water/100), color = "gray", 
             show.legend = F,  size = 4, alpha = 0.5) +
  
  geom_point(data = d_raw_out[d_raw_out$Vol_Water>0 & d_raw_out$Vol_Water_d<1 &
                                d_raw_out$MPa_Log10> -4,], 
             aes(y = abs(MPa), x = Vol_Water_d, color = Sample), 
             show.legend = F,  size = 4, alpha = 0.5) + 
  
  #scale_color_manual(values = c("#4D54E8", "#ECC01D", "#A2A197"))+ 

  ylab('Matric Potential [MPa]') +
  xlab('Soil Water Content [%]') +
  

  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                labels = trans_format("log10", math_format(10^.x)),
                limits = c(10^-4, 10^2))+
  annotation_logticks() +  
  theme(legend.position = "bottom",
        axis.text=element_text(size=30),
        axis.title=element_text(size=30),
        legend.title=element_text("Species",size=30),
        legend.text=element_text(size=30))

##//Dataset without some of the weird outliers
##//Cheat filter for when needed
dOut <- data.frame()
for(i in 1:length(d_raw_out$Sample)){
stringy <- strsplit(d_raw_out$Sample, split = "_")
site <- stringy[[i]][1]
plot <- stringy[[i]][2]
depth <- stringy[[i]][3]

dOut <- rbind(dOut, data.frame(Site = site,
                               Plot = plot,
                               Depth = depth) )
}

d_raw_out <- cbind(d_raw_out, dOut)

##//updating depths
Depth_cm <- ifelse(d_raw_out$Depth=="0cm", 0, d_raw_out$Depth)
Depth_cm <- ifelse(Depth_cm=="10cm", 10, Depth_cm)
Depth_cm <- ifelse(Depth_cm=="50cm", 50, Depth_cm)
Depth_cm <- ifelse(Depth_cm=="r1", 0, Depth_cm)
Depth_cm <- ifelse(Depth_cm=="r2", 0, Depth_cm)

d_raw_out$Depth_cm <- as.numeric(Depth_cm)


ggplot() +
  geom_point(data = d_raw_out[d_raw_out$Vol_Water>0 & d_raw_out$Vol_Water_d<1 &
                                d_raw_out$MPa_Log10> -4 & d_raw_out$Depth_cm==10,], 
             aes(y = abs(MPa), x = Vol_Water_d, color = Sample), 
             show.legend = T,  size = 4, alpha = 0.5) + 

  ylab('Matric Potential [MPa]') +
  xlab('Soil Water Content [%]') +
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                labels = trans_format("log10", math_format(10^.x)),
                limits = c(10^-4, 10^2))+
  annotation_logticks() +  
  theme(legend.position = "left",
        axis.text=element_text(size=30),
        axis.title=element_text(size=30),
        legend.title=element_text("Species",size=30),
        legend.text=element_text(size=30))

##//remove SN and SS for MMSF analysis but keep for Daniels analysis
##//0 cm curves look good
##//10 cm missing data from BC1 and BC4 has some outliers
##//50 cm BC4 & TDR1 has some outliers
##//Removing Outliers in TDR1_50cm
cc <- d_raw_out$Sample=="MMSF_TDR1_50cm" & d_raw_out$Vol_Water_d<=0.4 &
                                 d_raw_out$Vol_Water_d>=0.3

plot(d_raw_out$MPa_Log10[cc] ~ as.numeric(d_raw_out$Vol_Water_d[cc]))
d_raw_out$Vol_Water_d[cc] <- NA

##//Removing Outliers in BC4_50cm
cc <- d_raw_out$Sample=="MMSF_BC4_50cm" 
plot(d_raw_out$MPa_Log10[cc] ~ as.numeric(d_raw_out$Vol_Water_d[cc]))

dd <- d_raw_out$Sample=="MMSF_BC4_50cm" & d_raw_out$Vol_Water_d<=0.2 &                                    d_raw_out$MPa_Log10<= -1.5
points(d_raw_out$MPa_Log10[dd] ~ as.numeric(d_raw_out$Vol_Water_d[dd]), col = "red")
d_raw_out$Vol_Water_d[dd] <- NA

##//Removing Outliers in BC4_10cm
cc <- d_raw_out$Sample=="MMSF_BC4_10cm" 
plot(d_raw_out$MPa_Log10[cc] ~ as.numeric(d_raw_out$Vol_Water_d[cc]))

dd <- d_raw_out$Sample=="MMSF_BC4_10cm" & d_raw_out$Vol_Water_d>=0.2 & d_raw_out$Vol_Water_d<=0.4 &                                    d_raw_out$MPa_Log10<= -2
points(d_raw_out$MPa_Log10[dd] ~ as.numeric(d_raw_out$Vol_Water_d[dd]), col = "red")
d_raw_out$Vol_Water_d[dd] <- NA




ggplot() +
  geom_point(data = d_raw_out[d_raw_out$Vol_Water>0 & d_raw_out$Vol_Water_d<1 &
                                d_raw_out$MPa_Log10> -4 & d_raw_out$Depth_cm==50,], 
             aes(y = abs(MPa), x = as.numeric(Vol_Water_d), color = Sample), 
             show.legend = T,  size = 4, alpha = 0.5) + 

  ylab('Matric Potential [MPa]') +
  xlab('Soil Water Content [%]') +
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                labels = trans_format("log10", math_format(10^.x)),
                limits = c(10^-4, 10^2))+
  annotation_logticks() +  
  theme(legend.position = "left",
        axis.text=element_text(size=30),
        axis.title=element_text(size=30),
        legend.title=element_text("Species",size=30),
        legend.text=element_text(size=30))





cc <- d_raw_out$Vol_Water>0 & d_raw_out$Vol_Water_d<1 &
                                d_raw_out$MPa_Log10> -4

##//Subsetting raw data form model fitting
d_fitting <- d_raw_out[d_raw_out$Vol_Water>0 & d_raw_out$Vol_Water_d<1 &
                                d_raw_out$MPa_Log10> -4,]
##//Make sure pressures are all positive for analysis
d_fitting$MPa_Abs <- abs(d_fitting$MPa)

##//Van Genutchen model function
##//Currently simple nls model may move later
vg <- function(suction,thetas,thetar,a,n){
  
  ((thetas-thetar)/((((a*suction)^n)+1)^(1-(1/n))))+thetar

}

##Isolating Pressure and decimal VWC for surface sensors
x <- d_fitting$MPa_Abs[d_fitting$Depth_cm==0]
y <- d_fitting$Vol_Water_d[d_fitting$Depth_cm==0]

##//Note starting parameters are very sensitive (may need to tweak for each dataset)
fit_0 <- nls(y~vg(x,thetas,thetar,a,n),start=list(thetas=0.74,thetar=0.02,a=20,n=1.55))
##//Summary of model fit
summary(fit_0)
##//defining object to extract model parameters 
fit_sum_0 <- summary(fit_0)

##//Model parameters and error
thetas_0 = fit_sum_0$coefficients[1]
thetas_error_0 = fit_sum_0$coefficients[5]
thetar_0 = fit_sum_0$coefficients[2]
thetar_error_0 = fit_sum_0$coefficients[6]
alpha_0 = fit_sum_0$coefficients[3]
alpha_error_0 = fit_sum_0$coefficients[7]
n_0 = fit_sum_0$coefficients[4]
n_error_0 = fit_sum_0$coefficients[8]

##//Model estimates
myVWC <- seq(min(d_fitting$Vol_Water_d, na.rm = T), 
             max(d_fitting$Vol_Water_d, na.rm = T),
             length = 1000)
myPSI_0 <-  ( (  ((thetar_0- thetas_0) / (thetar_0 - myVWC)) ^ (n_0/(n_0-1)) - 1 ) ^(1/n_0) ) / alpha_0

##//Graphing dataframe
dOUT <- data.frame(myVWC, myPSI_0)

##Isolating Pressure and decimal VWC for 10 cm
x <- d_fitting$MPa_Abs[d_fitting$Depth_cm==10]
y <- d_fitting$Vol_Water_d[d_fitting$Depth_cm==10]

##//Note starting parameters are very sensitive (may need to tweak for each dataset)
fit_10 <- nls(y~vg(x,thetas,thetar,a,n),start=list(thetas=0.74,thetar=0.02,a=20,n=1.55))
##//Summary of model fit
summary(fit_10)
##//defining object to extract model parameters 
fit_sum_10 <- summary(fit_10)

##//Model parameters and error
thetas_10 = fit_sum_10$coefficients[1]
thetas_error_10 = fit_sum_10$coefficients[5]
thetar_10 = fit_sum_10$coefficients[2]
thetar_error_10 = fit_sum_10$coefficients[6]
alpha_10 = fit_sum_10$coefficients[3]
alpha_error_10 = fit_sum_10$coefficients[7]
n_10 = fit_sum_10$coefficients[4]
n_error_10 = fit_sum_10$coefficients[8]

##//Model estimates
myPSI_10 <-  ( (  ((thetar_10- thetas_10) / (thetar_10 - myVWC)) ^ (n_10/(n_10-1)) - 1 ) ^(1/n_10) ) / alpha_10

##//Graphing dataframe
dOUT <- cbind(dOUT, myPSI_10)

##Isolating Pressure and decimal VWC for 50 cm
x <- d_fitting$MPa_Abs[d_fitting$Depth_cm==50]
y <- d_fitting$Vol_Water_d[d_fitting$Depth_cm==50]

##//Note starting parameters are very sensitive (may need to tweak for each dataset)
fit_50 <- nls(y~vg(x,thetas,thetar,a,n),start=list(thetas=0.74,thetar=0.02,a=20,n=1.55))
##//Summary of model fit
summary(fit_50)
##//defining object to extract model parameters 
fit_sum_50 <- summary(fit_50)

##//Model parameters and error
thetas_50 = fit_sum_50$coefficients[1]
thetas_error_50 = fit_sum_50$coefficients[5]
thetar_50 = fit_sum_50$coefficients[2]
thetar_error_50 = fit_sum_50$coefficients[6]
alpha_50 = fit_sum_50$coefficients[3]
alpha_error_50 = fit_sum_50$coefficients[7]
n_50 = fit_sum_50$coefficients[4]
n_error_50 = fit_sum_50$coefficients[8]

##//Model estimates
myPSI_50 <-  ( (  ((thetar_50- thetas_50) / (thetar_50 - myVWC)) ^ (n_50/(n_50-1)) - 1 ) ^(1/n_50) ) / alpha_50

##//Graphing dataframe
dOUT <- cbind(dOUT, myPSI_50)




##//Plot the METER curves with the raw data
ggplot() +
   # geom_line(data = d_fit_out, 
   #          aes(y = MPa, x = Vol_Water / 100), color = "gray", 
   #           show.legend = F,  size = 4, alpha = 0.3) +
   geom_point(data = d_fitting,
             aes(y = abs(MPa), x = Vol_Water_d, color = Sample),
             show.legend = F,  size = 4, alpha = 0.2) +
   geom_line(data = dOUT, 
            aes(y = myPSI_0, x = myVWC), color = "black", 
             show.legend = F,  size = 5, alpha = 0.7) +
     geom_line(data = dOUT, 
            aes(y = myPSI_10, x = myVWC), color = "black", 
             show.legend = F,  size = 3, alpha = 0.7) +
     geom_line(data = dOUT, 
            aes(y = myPSI_50, x = myVWC), color = "black", 
             show.legend = F,  size = 1, alpha = 0.7) +
  
  ylab('Matric Potential [MPa]') +
  xlab('Soil Water Content [%]') +
  scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x),
                labels = trans_format("log10", math_format(10^.x)),
                limits = c(10^-4, 10^2))+
  annotation_logticks() +  
  theme(legend.position = "bottom",
        axis.text=element_text(size=30),
        axis.title=element_text(size=30),
        legend.title=element_text("Species",size=30),
        legend.text=element_text(size=30))

##//Model parameters dataframe
paramsOUT <- data.frame(Parameter = c("$\\theta{s}$",
                                      "$\\theta{r}$",
                                      "$\\alpha$",
                                      "n"),
                        Value = c(thetas, thetar, alpha, n),
                        Error = c(thetas_error, thetar_error, alpha_error, n_error))


paramsOUT %>%
  kableExtra::kbl(caption = "Van Genutchen Model Parameters") %>%
  kableExtra::kable_classic(full_width = F, html_font = "Cambria", font_size = 7)

knitr::kable(paramsOUT)




```


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
